### 2019-09-06 manuscript/manuscript.tex
G's changes

  \caption{A: The convergence correlation, averaged across replicate pairs,
    through time. Each line represents the convergence correlation
    $\mathrm{cor}(\Delta p_{s}, \Delta p_{s})$ from a starting reference
    generation $s$ to a later time $t$, which varies along the x-axis; each
  line corresponds to a row of the temporal convergence correlation matrix
depicted to the right.}

@@

Finally, we observed that in the \gc{longest study}  we   %run evolve-and-resequence 
analyzed \parencite{Barghi2019-qy}, some genome-wide temporal covariances
\gc{become} negative at future timepoints (see the first two rows in
Figure \ref{fig:figure-1} A). \gc{This shows that alleles that were on
average going up initially are no going down in frequency, i.e. that
the average direction of selection experienced by alleles has
flipped. This must reflect either a change in the environment or the
genetic background, due to changing epistatic relationships among
alleles or  recombination breaking up selective alleles.}
\gc{Such reversals of selective dynamics could be occuring at other time-points but} the
signal of a change in the direction of selection \gc{at particular
  loci} may be washed out when we calculate our  genome-wide \gc{average} temporal
covariances. To address this limitation, we
calculated \gc{the distribution of the} temporal covariances over
100kb genomic windows \gc{(Figure \ref{fig:figure-3}, pooling
across all replicates see Supplementary Figure \ref{suppfig:barghi-offset-replicate-panels} for individuals replicates).}
\gc{The}
covariance of each tile is noisy, \gc{due to sampling and genetic
  drift, shown in }. \gc{The neutral distribution of the covariance is
  complicated due to} linkage
disequilibria (which can occur over long physical distances in E\&R and
selection studies, \cite{Nuzhdin2013-gf,Baldwin-Brown2014-cl}). 
\gc{Thus} we have developed a permutation-based procedure that constructs a null
distribution by randomly flipping the signs of the    %of the
                                %genome-wide covariances as they would
                                %look if only neutral genetic drift was acting. We do this 
allele frequency changes per-genomic window. \gc{This destroys}  %%  GC bit about 1,000 times seems more like figgure caption or methods
the systematic covariances created by linked selection but creates a sampling
distribution of the covariances spuriously created by neutral genetic
drift while preserve the complex dependencies
between adjacent loci created by linkage disequilibrium (see Supplementary
Material Section \ref{supp:empirical-null} for more details on this approach).
This empirical neutral null distribution is conservative in the sense that the
variances of the covariances are wider than expected under drift
alone \gc{as they include the effect of selection on the allele
  frequency change within a time-interval, just not between
  time-intervals.} We see, Figure \ref{fig:figure-3} A and B, that
windowed temporal covariances between close timepoints are skewed positive (a
heavy right tail), while between more distant timepoints these windowed
temporal covariances tend to shift to become more negative (a heavy
left tail).
We quantified the degree to which the left and right
tails \gc{are inflated compared to the null distribution as a function
  of time}, and see excesses in both tails in Figure
\ref{fig:figure-3} C. This finding is also
robust to sign-permuting allele frequency changes on a chromosome-level, the
longest extent that gametic linkage disequilibria can extend {\bf ????} (Supplementary
Figure \ref{suppfig:barghi-tailprobs-seqid}).  \gc{We} see a striking
pattern that \gc{the windowed} covariances not only decay towards zero, but in fact become
negative through time, consistent with \gc{many} regions in the genome having had a
reversed fitness effect at later timepoints.

@@

  \caption{A, B: The distribution of temporal covariances calculated in 100kb
    genomic windows from the \textcite{Barghi2019-qy} study, plotted alongside
    an empirical neutral null distribution created by recalculating the
    windowed covariances on \gc{a 1000 sign permutions} allele frequency changes. The
    bin number is 88, chosen by cross validation (Supplementary Materials
    \ref{suppfig:barghi-cross-validation-binsize}). In subfigure A, windowed
    covariances $\cov(\Delta p_t, \Delta p_{t+k})$ are separated by $k=2 \times
    10$ generations and in subfigure B the covariances are separated by $k=4
    \times 10$ generations; each $k$ is an off-diagonal from the variance
    diagonal of the temporal covariance matrix (see cartoon of upper-triangle
    of covariance matrix in subfigures A and B, where the first diagonal is the
    variance, and the dark gray indicates which off-diagonal of the covariance
    matrix is plotted in the histograms). C: The lower and upper tail
    probabilities of the observed windowed covariances, at 20\% and 80\%
    quintiles of the empirical neutral null distribution, for varying time
    between allele frequency changes (i.e. which off-diagonal $k$). The
  confidence intervals are  $95\%$ block-bootstrap confidence interval, and the
light gray dashed line indicates the 20\% tail probability expected under the
neutral null.}

>>>>

  \caption{gc{{\bf A}}: The convergence correlation, averaged across replicate pairs,
    through time. Each line represents the convergence correlation
    $\mathrm{cor}(\Delta p_{s}, \Delta p_{s})$ from a starting reference
    generation $s$ to a later time $t$, which varies along the x-axis; each
  line corresponds to a row of the temporal convergence correlation matrix
depicted to the right.  \gc{{\bf B}: The convergence covariance between
individual pairs of replicates in the \textcite{Kelly2019-dc} data. {\bf C}:  The convergence covariance between
individual pairs of replicates in \parencite{Castro2019-uk} data, for
the two selection lines  (LS1 and LS2) and the control (Ctrl).}}

@@

Finally, we observed that in the \gc{longest study}  we   %run evolve-and-resequence 
analyzed \parencite{Barghi2019-qy}, some genome-wide temporal covariances
\gc{become} negative at future timepoints (see the first two rows in
Figure \ref{fig:figure-1} A). \gc{This shows that alleles that were on
average going up initially are no going down in frequency, i.e. that
the average direction of selection experienced by alleles has
flipped. This must reflect either a change in the environment or the
genetic background, due to changing epistatic relationships among
alleles or  recombination breaking up selective alleles.}
\gc{Such reversals of selective dynamics could be occuring at other time-points but} the
signal of a change in the direction of selection \gc{at particular
  loci} may be washed out when we calculate our  genome-wide \gc{average} temporal
covariances. To address this limitation, we
calculated \gc{the distribution of the} temporal covariances over
100kb genomic windows \gc{(Figure \ref{fig:figure-3}, pooling
across all replicates see Supplementary Figure \ref{suppfig:barghi-offset-replicate-panels} for individuals replicates).}
\gc{The}
covariance of each tile \gc{will be} noisy, \gc{due to sampling and genetic
  drift, and the neutral distribution of the covariance is
  complicated due to} linkage
disequilibria (which can occur over long physical distances in E\&R and
selection studies, \cite{Nuzhdin2013-gf,Baldwin-Brown2014-cl}). 
\gc{Thus} we have developed a permutation-based procedure that constructs a null
distribution by randomly flipping the signs of the    %of the
                                %genome-wide covariances as they would
                                %look if only neutral genetic drift was acting. We do this 
allele frequency changes per-genomic window. \gc{This destroys}  %%  GC bit about 1,000 times seems more like figgure caption or methods
the systematic covariances created by linked selection but creates a sampling
distribution of the covariances spuriously created by neutral genetic
drift while preserve the complex dependencies
between adjacent loci created by linkage disequilibrium (see Supplementary
Material Section \ref{supp:empirical-null} for more details on this approach).
This empirical neutral null distribution is conservative in the sense that the
variances of the covariances are wider than expected under drift
alone \gc{as they include the effect of selection on the allele
  frequency change within a time-interval, just not between
  time-intervals.} We see, Figure \ref{fig:figure-3} A and B, that
windowed temporal covariances between close timepoints are skewed positive (a
heavy right tail), while between more distant timepoints these windowed
temporal covariances tend to shift to become more negative (a heavy
left tail).
We quantified the degree to which the left and right
tails \gc{are inflated compared to the null distribution as a function
  of time}, and see excesses in both tails in Figure
\ref{fig:figure-3} C. This finding is also
robust to sign-permuting allele frequency changes on a chromosome-level, the
longest extent that gametic linkage disequilibria can extend {\bf ????} (Supplementary
Figure \ref{suppfig:barghi-tailprobs-seqid}).  \gc{We} see a striking
pattern that \gc{the windowed} covariances not only decay towards zero, but in fact become
negative through time, consistent with \gc{many} regions in the genome having had a
reversed fitness effect at later timepoints.

@@

  \caption{A, B: The distribution of temporal covariances calculated in 100kb
    genomic windows from the \textcite{Barghi2019-qy} study, plotted alongside
    an empirical neutral null distribution created by recalculating the
    windowed covariances on \gc{a 1000 sign permutions of} allele
    frequency changes \gc{within tiles}. The
    \gc{histogram} bin number is 88, chosen by cross validation (Supplementary Materials
    \ref{suppfig:barghi-cross-validation-binsize}). In subfigure A, windowed
    covariances $\cov(\Delta p_t, \Delta p_{t+k})$ are separated by $k=2 \times
    10$ generations and in subfigure B the covariances are separated by $k=4
    \times 10$ generations; each $k$ is an off-diagonal from the variance
    diagonal of the temporal covariance matrix (see cartoon of upper-triangle
    of covariance matrix in subfigures A and B, where the first diagonal is the
    variance, and the dark gray indicates which off-diagonal of the covariance
    matrix is plotted in the histograms). C: The lower and upper tail
    probabilities of the observed windowed covariances, at 20\% and 80\%
    quintiles of the empirical neutral null distribution, for varying time
    between allele frequency changes (i.e. which off-diagonal $k$). The
  confidence intervals are  $95\%$ block-bootstrap confidence interval, and the
light gray dashed line indicates the 20\% tail probability expected under the
neutral null.}
